---
title: Evaluate Score
---

# Tutorial

## Basic evaluation

- modify `./TAD STRI/Matrix_Simulator_Template_APEC_scaleback.xlsx`: copy
formula from cell AF1140 to cells AH1140 and AJ1140 in sheet `Indicator`
(LineID:`90808`, CH1:`CR.1`, CH2:`1_20_6`) )
- set `cache` to `FALSE` in code block `generate-data` (copied from
  `generate_simulator` function defined in `./R/generator.R`)
- re-generate this document
- modify numans value for countryname:`Austria`, LineID:`90401`,
  QuestionCode:`1_25_1`, e.g. from 0 -> 0.4
- re-generate this document
- observe change in result: `Score` for countryname:`Austria` is now `0.4`


## User-supplied function

- open `./TAD STRI/Matrix_Simulator_Template_APEC_scaleback.xlsx`, sheet `Indicator`
- insert following text in cell AJ1140 (column: `Score2`, LineID:`90808`,
CH1:`CR.1`, CH2:`1_20_6`)
- start application
- select "Courier services", "Australia"
- expand 1st table "Restrictions on foreign entry", scroll down to `1_20_6 Cross-border data flows: transfer of data is prohibited`, observe EditedScore = 2
- expand last table "Regulatory transparency", modify value `5_6_1 Number of mandatory procedures to register a company`: reducing from 3 to 1 will reduce the sum (7.2 - 2 = 5.2) below 6 and decrease the EditedScore of `1_20_6` from 2 to 1; increasing from 3 to 7 will increase the sum (7.2 + 4 = 11.2) above the next step (11) and result in an EditedScore of `1_20_6` of 3.

```
user_fun(breaks=c(4,6,11,16,21,26),scores=c(0:6),num94106,num94200,num94300,num94400)
```

- the custom user functions must be loaded both before generating the
  application data and at application runtime:
  `source("../inst/app/src/lib/custom_funs.R")`
- generate the application (see `setup.Rmd`) and start the application (e.g.
  using `scripts/run-app.sh`)
- within the application, check the value in STRI Sector "Courier services",
  "Australia", "Restrictions on foreign entry" (expand the table), the score of
  question `1_20_6` "Cross-border data flows: transfer of data is prohibited"
  should be 2 with answer "No" and 1 with answer "Yes"
- after re-generating and running the application, modify the custorm user
  function and return the value "5": `return(5)`. Now restart the application
- the initial score for answer "No" is still 2, when changing the answer to
  "Yes", the score still becomes 1. When changing back to "No", the answer is
  recalculated and the score 5 is returned.

```{r}

#' @examples
#' nums <- c(422:465)
#' breaks <- c(4, 6, 11, 16, 21, 26)
#' scores <- c(0:6)
#'
#' obj <- e$numals_env[["CR"]][["Australia"]]
#' ## members <- ls(obj)
#' nums <- c(94106, 94200, 94300, 94400)
#' members <- paste0("num", nums)
#' sapply(members, function(x) obj[[x]]) %>% sum()
#'
#' attach(obj)
#' user_fun(breaks, scores)
#' user_fun(breaks=c(4, 6, 11, 16, 21, 26), scores=c(0:6))
#' detach(obj)
#' num94106 <- 1
#' user_fun(breaks, scores, num94106, num94200, num94300, num94400)

user_fun <- function(breaks, scores, ...) {
    ## return -1 if any value is missing
    ## if(any(num94106==-1, num94200==-1, num94300==-1, num94400==-1)) return(-1)
    ## my_sum <- sum(num94106, num94200, num94300, num94400)
    if (any(sapply(list(...), function(x) x==-1))) return(-1)
    my_sum <- sum(...)

    res <-
        data.frame(lower = c(0, breaks),
                   upper = c(breaks, Inf),
                   score = scores,
                   value = my_sum
                   ) %>%
        dplyr::mutate(between = ifelse(value > lower & value <= upper,
                                       TRUE, FALSE)) %>%
        dplyr::filter(between == TRUE) %>%
        dplyr::pull(score)

    return(res) # for testing, change to "return(5)"
}

```

```{r setup, echo=FALSE, message=FALSE}

## library(dplyr)
devtools::load_all()

excel_template_path <- "../TAD STRI/Matrix_Simulator_Template_APEC_scaleback.xlsx"
target_app_path <- "../stri_apec"

```

```{r generate-data, echo=FALSE, message=FALSE, cache=FALSE}

## Data import and initial values conversion
template <- import_template_data(excel_template_path)
template$Hierarchy <- convert_to_upper(template$Hierarchy)
template$Data <- convert_empty_to_na(template$Data)
template$Indicator <- convert_empty_to_na(template$Indicator) %>%
    convert_to_character(match_cols(., "Cond|Score"))

levels_meta <- get_levels_meta(template$Hierarchy)

country_indicator_data <- dplyr::left_join(template$Data, template$Indicator, by = "LineID") %>%
    dplyr::rename(`UI.Element` = `UI Element`) %>%
    dplyr::filter(!is.na(LineID)) %>%
    dplyr::mutate(LineID = paste0("num", trimws(LineID))) %>%
    dplyr::mutate_at(vars(dplyr::starts_with("Cond")), ~numans_to_numline(., LineID)) %>%
    dplyr::mutate_at(vars(dplyr::starts_with("Score")), ~numans_to_numline(., LineID))

numals_env <- get_numals_vals(country_indicator_data, levels_meta)

## country_indicator_data %>% dplyr::filter(LineID == "num90808") %>% dplyr::select(dplyr::starts_with("Score"))
save(country_indicator_data, numals_env, levels_meta, file = "../example/compute_score_data.rda")

```

```{r}

e <- rlang::env()
load(file = "../example/compute_score_data.rda", envir = e)

country_indicator_data <- e$country_indicator_data %>%
    ## dplyr::filter(countryname == "Australia") %>%
    dplyr::filter(CH1 == "CR.1" & CH2 %in% c("1_20_6")) %>%
    dplyr::select(CH0, CH1, CH2, countryname, dplyr::starts_with("Cond"), dplyr::starts_with("Score"))

res <- compute_score(country_indicator_data, e$numals_env, e$levels_meta)
## (1-num90401)*0 + num90401*1
## numans for LineID 90401
## AUS: 0.233
## AUT: 0 -> e.g. 0.4
## BRA: 0.333333333
## CAN: 0.233333333
## CHE: 0.2
## CHL: 0.333
## CHN: 0.666666667

res %>%
    dplyr::select(CH0, CH1, CH2, countryname, Score) %>%
    knitr::kable()

```

```{r, include=FALSE}

#' e <- rlang::env()
#' load(file = "../example/compute_score_data.rda", envir = e)
#' str(e$country_indicator_data)
#' e$country_indicator_data %>% dplyr::filter(OH2 == 1139) %>% dplyr::select(dplyr::starts_with("Score"))
#' country_indicator_data <- e$country_indicator_data %>% dplyr::filter(countryname == "Australia") %>% dplyr::select(CH0, CH1, CH2, countryname, dplyr::starts_with("Cond"), dplyr::starts_with("Score"))
#' ## country_indicator_data <- e$country_indicator_data %>% head() %>% dplyr::mutate(Score0 = ifelse(Score0 == "no", 0, Score0))
#' str(country_indicator_data)
#'
#' numals_env <- e$numals_env
#' levels_meta <- e$levels_meta
#' res <- compute_score(country_indicator_data, numals_env, levels_meta)
#' str(res)
#' res %>% dplyr::filter(!Score %in% c(0,1)) %>% dplyr::pull(Score)
#' write.csv(res, file = "../example/compute_score_res.csv", row.names = FALSE)
#' numals_env[["CS"]][["Belgium"]]

```
